---
title: "Master"
output: html_document
date: "2023-08-27"
---

Experiment results analysis 

Installing packages
```{r}
library(nnet)
library(readxl)
library(tidyverse)
library(magrittr)
library(tidyr)
library(stargazer)
library(dplyr)  

```

Reading data and converting 'countries' to binary
```{r}

data <- read_excel("/Users/Masha/Desktop/thesis_data/master_thesis/survey_15_june.xlsx")

#Converting countries to binary
data$country_live_Ukraine <- ifelse(data$country_live == "Ukraine", 1, 0)
data$country_origin_Ukraine <- ifelse(data$country_origin == "Ukraine", 1, 0)

```

Summary statistics
```{r}

summary_data <- summary(data)
print(summary_data)

gender_table <- table(data$gender)
print(gender_table)
gender_percentages <- prop.table(gender_table)
print(gender_percentages)

```

*Welch's two-sample t-tests:*

Comparison of donations to each cause under *positive vs negative treatments*
```{r}
#Rebuilding cause
pos_rebuilding <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "rebuilding"]
neg_rebuilding <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "rebuilding"]
t_test_result <- t.test(pos_rebuilding, neg_rebuilding)
print(t_test_result)

#Keep money for yourself option
pos_keep <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "keep"]
neg_keep <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "keep"]
t_test_result <- t.test(pos_keep, neg_keep)
print(t_test_result)

#Defence cause
pos_defence <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "defence"]
neg_defence <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "defence"]
t_test_result <- t.test(pos_defence, neg_defence)
print(t_test_result)

#Humanitarian help cause
pos_humanitarian <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "humanitarian"]
neg_humanitarian <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "humanitarian"]
t_test_result <- t.test(pos_humanitarian, neg_humanitarian)
print(t_test_result)
```

Cmparison of donations to each cause under *high-energy vs low-energy treatments*
```{r}
#Rebuilding cause
low_rebuilding <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "rebuilding"]
high_rebuilding <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "rebuilding"]
t_test_result <- t.test(low_rebuilding, high_rebuilding)
print(t_test_result)

#Humanitarian help cause
low_humanitarian <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "humanitarian"]
high_humanitarian <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "humanitarian"]
t_test_result <- t.test(low_humanitarian, high_humanitarian)
print(t_test_result)

#Keep money to yourself option
low_keep <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "keep"]
high_keep <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "keep"]
t_test_result <- t.test(low_keep, high_keep)
print(t_test_result)

#Defence cause
low_defence <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "defence"]
high_defence <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "defence"]
t_test_result <- t.test(low_defence, high_defence)
print(t_test_result)
```

Comparison of donations to certain cause under *each treatment vs three other treatments*
```{r}
# Release of POWs treatment vs other treatments
#####
pows_defence <- data[data$treatment == "Release of POWs", "defence"]
other_defence <- data[data$treatment != "Release of POWs", "defence"]
t_test_result <- t.test(pows_defence, other_defence)
print(t_test_result)

pows_keep <- data[data$treatment == "Release of POWs", "keep"]
other_keep <- data[data$treatment != "Release of POWs", "keep"]
t_test_result <- t.test(pows_keep, other_keep)
print(t_test_result)

pows_humanitarian <- data[data$treatment == "Release of POWs", "humanitarian"]
other_humanitarian <- data[data$treatment != "Release of POWs", "humanitarian"]
t_test_result <- t.test(pows_humanitarian, other_humanitarian)
print(t_test_result)

pows_rebuilding <- data[data$treatment == "Release of POWs", "rebuilding"]
other_rebuilding <- data[data$treatment != "Release of POWs", "rebuilding"]
t_test_result <- t.test(pows_rebuilding, other_rebuilding)
print(t_test_result)
#####

# Drama theater treatment vs other treatments
#####
theater_rebuilding <- data[data$treatment == "Drama Theater", "rebuilding"]
other_rebuilding <- data[data$treatment != "Drama Theater", "rebuilding"]
t_test_result <- t.test(theater_rebuilding, other_rebuilding)
print(t_test_result)

theater_humanitarian <- data[data$treatment == "Drama Theater", "humanitarian"]
other_humanitarian <- data[data$treatment != "Drama Theater", "humanitarian"]
t_test_result <- t.test(theater_humanitarian, other_humanitarian)
print(t_test_result)

theater_keep <- data[data$treatment == "Drama Theater", "keep"]
other_keep <- data[data$treatment != "Drama Theater", "keep"]
t_test_result <- t.test(theater_keep, other_keep)
print(t_test_result)

theater_defence <- data[data$treatment == "Drama Theater", "defence"]
other_defence <- data[data$treatment != "Drama Theater", "defence"]
t_test_result <- t.test(theater_defence, other_defence)
print(t_test_result)
#####

# Ukraine shelling treatment vs other treatments
#####
shelling_defence <- data[data$treatment == "Ukraine Shelling", "defence"]
other_defence <- data[data$treatment != "Ukraine Shelling", "defence"]
t_test_result <- t.test(shelling_defence, other_defence)
print(t_test_result)

shelling_keep <- data[data$treatment == "Ukraine Shelling", "keep"]
other_keep <- data[data$treatment != "Ukraine Shelling", "keep"]
t_test_result <- t.test(shelling_keep, other_keep)
print(t_test_result)

shelling_humanitarian <- data[data$treatment == "Ukraine Shelling", "humanitarian"]
other_humanitarian <- data[data$treatment != "Ukraine Shelling", "humanitarian"]
t_test_result <- t.test(shelling_humanitarian, other_humanitarian)
print(t_test_result)

shelling_rebuilding <- data[data$treatment == "Ukraine Shelling", "rebuilding"]
other_rebuilding <- data[data$treatment != "Ukraine Shelling", "rebuilding"]
t_test_result <- t.test(shelling_rebuilding, other_rebuilding)
print(t_test_result)
#####

# Kherson Liberation treatment vs other treatments
#####
kherson_defence <- data[data$treatment == "Kherson Liberation", "defence"]
other_defence <- data[data$treatment != "Kherson Liberation", "defence"]
t_test_result <- t.test(kherson_defence, other_defence)
print(t_test_result)

kherson_keep <- data[data$treatment == "Kherson Liberation", "keep"]
other_keep <- data[data$treatment != "Kherson Liberation", "keep"]
t_test_result <- t.test(kherson_keep, other_keep)
print(t_test_result)

kherson_humanitarian <- data[data$treatment == "Kherson Liberation", "humanitarian"]
other_humanitarian <- data[data$treatment != "Kherson Liberation", "humanitarian"]
t_test_result <- t.test(kherson_humanitarian, other_humanitarian)
print(t_test_result)

kherson_rebuilding <- data[data$treatment == "Kherson Liberation", "rebuilding"]
other_rebuilding <- data[data$treatment != "Kherson Liberation", "rebuilding"]
t_test_result <- t.test(kherson_rebuilding, other_rebuilding)
print(t_test_result)
#####
```

Comparison of donations to each cause for subset of *Ukrainians vs subset of non-Ukrainians*
```{r}
#Country_origin
#####
#Defence cause
ukr_defence <- data[data$country_origin_Ukraine == "1", "defence"]
non_ukr_defence <- data[data$country_origin_Ukraine == "0", "defence"]
t_test_result <- t.test(ukr_defence, non_ukr_defence)
print(t_test_result)

#Humanitarian help cause
ukr_humanitarian <- data[data$country_origin_Ukraine == "1", "humanitarian"]
non_ukr_humanitarian <- data[data$country_origin_Ukraine == "0", "humanitarian"]
t_test_result <- t.test(ukr_humanitarian, non_ukr_humanitarian)
print(t_test_result)

#Rebuilding cause
ukr_rebuilding <- data[data$country_origin_Ukraine == "1", "rebuilding"]
non_ukr_rebuilding <- data[data$country_origin_Ukraine == "0", "rebuilding"]
t_test_result <- t.test(ukr_rebuilding, non_ukr_rebuilding)
print(t_test_result)

#Keep money for yourself option
ukr_keep <- data[data$country_origin_Ukraine == "1", "keep"]
non_ukr_keep <- data[data$country_origin_Ukraine == "0", "keep"]
t_test_result <- t.test(ukr_keep, non_ukr_keep)
print(t_test_result)
#####

#Country_live
#####

#Defence cause
ukr_defence <- data[data$country_live_Ukraine == "1", "defence"]
non_ukr_defence <- data[data$country_live_Ukraine == "0", "defence"]
t_test_result <- t.test(ukr_defence, non_ukr_defence)
print(t_test_result)

#Humanitarian help cause
ukr_humanitarian <- data[data$country_live_Ukraine == "1", "humanitarian"]
non_ukr_humanitarian <- data[data$country_live_Ukraine == "0", "humanitarian"]
t_test_result <- t.test(ukr_humanitarian, non_ukr_humanitarian)
print(t_test_result)

#Rebuilding cause
ukr_rebuilding <- data[data$country_live_Ukraine == "1", "rebuilding"]
non_ukr_rebuilding <- data[data$country_live_Ukraine == "0", "rebuilding"]
t_test_result <- t.test(ukr_rebuilding, non_ukr_rebuilding)
print(t_test_result)

#Keep money for yourself option
ukr_keep <- data[data$country_live_Ukraine == "1", "keep"]
non_ukr_keep <- data[data$country_live_Ukraine == "0", "keep"]
t_test_result <- t.test(ukr_keep, non_ukr_keep)
print(t_test_result)
#####
```

Comparison of donations to each cause for subset of *females versus subset of males*
```{r}
#Defence cause
female_defence <- data[data$gender == "female", "defence"]
male_defence <- data[data$gender == "male", "defence"]
t_test_result <- t.test(female_defence, male_defence)
print(t_test_result)

#Humanitarian help cause
female_humanitarian <- data[data$gender == "female", "humanitarian"]
male_humanitarian <- data[data$gender == "male", "humanitarian"]
t_test_result <- t.test(female_humanitarian, male_humanitarian)
print(t_test_result)

#Rebuilding cause
female_rebuilding <- data[data$gender == "female", "rebuilding"]
male_rebuilding <- data[data$gender == "male", "rebuilding"]
t_test_result <- t.test(female_rebuilding, male_rebuilding)
print(t_test_result)

#Keep money for yourself option
female_keep <- data[data$gender == "female", "keep"]
male_keep <- data[data$gender == "male", "keep"]
t_test_result <- t.test(female_keep, male_keep)
print(t_test_result)

```

*OLS Regressions*
# Doing ANOVA to see if there is effect of treatment on induced emotions
anova_result <- aov(anger + fear + joy + sadness + disgust + relief ~ treatment, data = data)
summary(anova_result)

