---
title: "Master"
output: html_document
date: "2023-08-27"
---

Experiment results analysis 

Installing packages
```{r}
library(nnet)
library(readxl)
library(tidyverse)
library(magrittr)
library(tidyr)
library(dplyr)  

```

Reading data and converting 'countries' to binary
```{r}

data <- read_excel("/Users/Masha/Desktop/thesis_data/master_thesis/survey_15_june.xlsx")

#Converting countries to binary
data$country_live_Ukraine <- ifelse(data$country_live == "Ukraine", 1, 0)
data$country_origin_Ukraine <- ifelse(data$country_origin == "Ukraine", 1, 0)

```

Summary statistics
```{r}

summary_data <- summary(data)
summary_data

gender_table <- table(data$gender)
gender_table

gender_percentages <- prop.table(gender_table)
gender_percentages

```

*Welch's two-sample t-tests:*

Comparison of donations to each cause under positive vs negative treatments
```{r}
#Rebuilding cause
pos_rebuilding <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "rebuilding"]
neg_rebuilding <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "rebuilding"]
t_test_result_rebuilding <- t.test(pos_rebuilding, neg_rebuilding)
t_test_result_rebuilding

#Keep money for yourself option
pos_keep <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "keep"]
neg_keep <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "keep"]
t_test_result_keep <- t.test(pos_keep, neg_keep)
t_test_result_keep

#Defence cause
pos_defence <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "defence"]
neg_defence <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "defence"]
t_test_result_defence <- t.test(pos_defence, neg_defence)
t_test_result_defence

#Humanitarian help cause
pos_humanitarian <- data[data$treatment != "Drama Theater" & data$treatment != "Ukraine Shelling", "humanitarian"]
neg_humanitarian <- data[data$treatment != "Kherson Liberation" & data$treatment != "Release of POWs", "humanitarian"]
t_test_result_humanitarian <- t.test(pos_humanitarian, neg_humanitarian)
t_test_result_humanitarian
```

Comparison of donations to each cause under high-energy vs low-energy treatments
```{r}
#Rebuilding cause
low_rebuilding <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "rebuilding"]
high_rebuilding <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "rebuilding"]
t_test_result <- t.test(low_rebuilding, high_rebuilding)
t_test_result

#Humanitarian help cause
low_humanitarian <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "humanitarian"]
high_humanitarian <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "humanitarian"]
t_test_result <- t.test(low_humanitarian, high_humanitarian)
t_test_result

#Keep money to yourself option
low_keep <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "keep"]
high_keep <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "keep"]
t_test_result <- t.test(low_keep, high_keep)
t_test_result

#Defence cause
low_defence <- data[data$treatment != "Kherson Liberation" & data$treatment != "Ukraine Shelling", "defence"]
high_defence <- data[data$treatment != "Drama Theater" & data$treatment != "Release of POWs", "defence"]
t_test_result <- t.test(low_defence, high_defence)
t_test_result
```

Comparison of donations to certain cause under each treatment vs three other treatments
```{r}
# Release of POWs treatment vs other treatments
#####
pows_defence <- data[data$treatment == "Release of POWs", "defence"]
other_defence <- data[data$treatment != "Release of POWs", "defence"]
t_test_result <- t.test(pows_defence, other_defence)
t_test_result

pows_keep <- data[data$treatment == "Release of POWs", "keep"]
other_keep <- data[data$treatment != "Release of POWs", "keep"]
t_test_result <- t.test(pows_keep, other_keep)
t_test_result

pows_humanitarian <- data[data$treatment == "Release of POWs", "humanitarian"]
other_humanitarian <- data[data$treatment != "Release of POWs", "humanitarian"]
t_test_result <- t.test(pows_humanitarian, other_humanitarian)
t_test_result

pows_rebuilding <- data[data$treatment == "Release of POWs", "rebuilding"]
other_rebuilding <- data[data$treatment != "Release of POWs", "rebuilding"]
t_test_result <- t.test(pows_rebuilding, other_rebuilding)
t_test_result
#####

# Drama theater treatment vs other treatments
#####
theater_rebuilding <- data[data$treatment == "Drama Theater", "rebuilding"]
other_rebuilding <- data[data$treatment != "Drama Theater", "rebuilding"]
t_test_result <- t.test(theater_rebuilding, other_rebuilding)
t_test_result

theater_humanitarian <- data[data$treatment == "Drama Theater", "humanitarian"]
other_humanitarian <- data[data$treatment != "Drama Theater", "humanitarian"]
t_test_result <- t.test(theater_humanitarian, other_humanitarian)
t_test_result

theater_keep <- data[data$treatment == "Drama Theater", "keep"]
other_keep <- data[data$treatment != "Drama Theater", "keep"]
t_test_result <- t.test(theater_keep, other_keep)
t_test_result

theater_defence <- data[data$treatment == "Drama Theater", "defence"]
other_defence <- data[data$treatment != "Drama Theater", "defence"]
t_test_result <- t.test(theater_defence, other_defence)
t_test_result
#####

# Ukraine shelling treatment vs other treatments
#####
shelling_defence <- data[data$treatment == "Ukraine Shelling", "defence"]
other_defence <- data[data$treatment != "Ukraine Shelling", "defence"]
t_test_result <- t.test(shelling_defence, other_defence)
t_test_result

shelling_keep <- data[data$treatment == "Ukraine Shelling", "keep"]
other_keep <- data[data$treatment != "Ukraine Shelling", "keep"]
t_test_result <- t.test(shelling_keep, other_keep)
t_test_result

shelling_humanitarian <- data[data$treatment == "Ukraine Shelling", "humanitarian"]
other_humanitarian <- data[data$treatment != "Ukraine Shelling", "humanitarian"]
t_test_result <- t.test(shelling_humanitarian, other_humanitarian)
t_test_result

shelling_rebuilding <- data[data$treatment == "Ukraine Shelling", "rebuilding"]
other_rebuilding <- data[data$treatment != "Ukraine Shelling", "rebuilding"]
t_test_result <- t.test(shelling_rebuilding, other_rebuilding)
t_test_result
#####

# Kherson Liberation treatment vs other treatments
#####
kherson_defence <- data[data$treatment == "Kherson Liberation", "defence"]
other_defence <- data[data$treatment != "Kherson Liberation", "defence"]
t_test_result <- t.test(kherson_defence, other_defence)
t_test_result

kherson_keep <- data[data$treatment == "Kherson Liberation", "keep"]
other_keep <- data[data$treatment != "Kherson Liberation", "keep"]
t_test_result <- t.test(kherson_keep, other_keep)
t_test_result

kherson_humanitarian <- data[data$treatment == "Kherson Liberation", "humanitarian"]
other_humanitarian <- data[data$treatment != "Kherson Liberation", "humanitarian"]
t_test_result <- t.test(kherson_humanitarian, other_humanitarian)
t_test_result

kherson_rebuilding <- data[data$treatment == "Kherson Liberation", "rebuilding"]
other_rebuilding <- data[data$treatment != "Kherson Liberation", "rebuilding"]
t_test_result <- t.test(kherson_rebuilding, other_rebuilding)
t_test_result
#####
```

Comparison of donations to each cause for subset of Ukrainians vs subset of non-Ukrainians
```{r}
#Country_origin
#####
#Defence cause
ukr_defence <- data[data$country_origin_Ukraine == "1", "defence"]
non_ukr_defence <- data[data$country_origin_Ukraine == "0", "defence"]
t_test_result <- t.test(ukr_defence, non_ukr_defence)
t_test_result

#Humanitarian help cause
ukr_humanitarian <- data[data$country_origin_Ukraine == "1", "humanitarian"]
non_ukr_humanitarian <- data[data$country_origin_Ukraine == "0", "humanitarian"]
t_test_result <- t.test(ukr_humanitarian, non_ukr_humanitarian)
t_test_result

#Rebuilding cause
ukr_rebuilding <- data[data$country_origin_Ukraine == "1", "rebuilding"]
non_ukr_rebuilding <- data[data$country_origin_Ukraine == "0", "rebuilding"]
t_test_result <- t.test(ukr_rebuilding, non_ukr_rebuilding)
t_test_result

#Keep money for yourself option
ukr_keep <- data[data$country_origin_Ukraine == "1", "keep"]
non_ukr_keep <- data[data$country_origin_Ukraine == "0", "keep"]
t_test_result <- t.test(ukr_keep, non_ukr_keep)
t_test_result
#####

#Country_live
#####

#Defence cause
ukr_defence <- data[data$country_live_Ukraine == "1", "defence"]
non_ukr_defence <- data[data$country_live_Ukraine == "0", "defence"]
t_test_result <- t.test(ukr_defence, non_ukr_defence)
t_test_result

#Humanitarian help cause
ukr_humanitarian <- data[data$country_live_Ukraine == "1", "humanitarian"]
non_ukr_humanitarian <- data[data$country_live_Ukraine == "0", "humanitarian"]
t_test_result <- t.test(ukr_humanitarian, non_ukr_humanitarian)
t_test_result

#Rebuilding cause
ukr_rebuilding <- data[data$country_live_Ukraine == "1", "rebuilding"]
non_ukr_rebuilding <- data[data$country_live_Ukraine == "0", "rebuilding"]
t_test_result <- t.test(ukr_rebuilding, non_ukr_rebuilding)
t_test_result

#Keep money for yourself option
ukr_keep <- data[data$country_live_Ukraine == "1", "keep"]
non_ukr_keep <- data[data$country_live_Ukraine == "0", "keep"]
t_test_result <- t.test(ukr_keep, non_ukr_keep)
t_test_result
#####
```

Comparison of donations to each cause for subset of females versus subset of males
```{r}
#Defence cause
female_defence <- data[data$gender == "female", "defence"]
male_defence <- data[data$gender == "male", "defence"]
t_test_result <- t.test(female_defence, male_defence)
t_test_result

#Humanitarian help cause
female_humanitarian <- data[data$gender == "female", "humanitarian"]
male_humanitarian <- data[data$gender == "male", "humanitarian"]
t_test_result <- t.test(female_humanitarian, male_humanitarian)
t_test_result

#Rebuilding cause
female_rebuilding <- data[data$gender == "female", "rebuilding"]
male_rebuilding <- data[data$gender == "male", "rebuilding"]
t_test_result <- t.test(female_rebuilding, male_rebuilding)
t_test_result

#Keep money for yourself option
female_keep <- data[data$gender == "female", "keep"]
male_keep <- data[data$gender == "male", "keep"]
t_test_result <- t.test(female_keep, male_keep)
t_test_result

```

*OLS Regressions*

OLS Regressions for emotions influence on donation amounts to each cause 
```{r}
#Not including treatment
#####
model_keep <- lm(keep ~ joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_keep)

model_hum <- lm(humanitarian ~ joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_hum)

model_def <- lm(defence ~ joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_def)

model_reb <- lm(rebuilding ~ joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_reb)
#####

#Including treatment
#####
model_keep_tr <- lm(keep ~ treatment + joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_keep_tr)

model_hum_tr <- lm(humanitarian ~ treatment + joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_hum_tr)

model_def_tr <- lm(defence ~ treatment + joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_def_tr)

model_reb_tr <- lm(rebuilding ~ treatment + joy + relief + anger + fear + sadness + disgust + age + gender + country_origin_Ukraine, data = data)
summary(model_reb_tr)
#####
```

OLS Regressions for treatment influence on donation amounts to each cause 
```{r}
#Setting Drama Theater as reference category
data$treatment <- factor(data$treatment)
data$treatment <- relevel(data$treatment, ref = "Drama Theater")

model_keep<- lm(keep ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_keep)

model_hum <- lm(humanitarian ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_hum)

model_def <- lm(defence ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_def)

model_reb <- lm(rebuilding ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_reb)

#Testing other reference categories

#Ukraine Shelling as a reference category
#####
data$treatment <- factor(data$treatment)
data$treatment <- relevel(data$treatment, ref = "Ukraine Shelling")

model_keep_3 <- lm(keep ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_keep_3)

model_hum_3 <- lm(humanitarian ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_hum_3)

model_def_3 <- lm(defence ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_def_3)

model_reb_3 <- lm(rebuilding ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_reb_3)
#####

#Release of POWs as a reference category
#####
data$treatment <- factor(data$treatment)
data$treatment <- relevel(data$treatment, ref = "Release of POWs")

model_keep_4 <- lm(keep ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_keep_4)

model_hum_4 <- lm(humanitarian ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_hum_4)

model_def_4 <- lm(defence ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_def_4)

model_reb_4 <- lm(rebuilding ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_reb_4)
#####

#Kherson Liberation as a reference category
#####
data$treatment <- factor(data$treatment)
data$treatment <- relevel(data$treatment, ref = "Kherson Liberation")

model_keep_5 <- lm(keep ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_keep_5)

model_hum_5 <- lm(humanitarian ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_hum_5)

model_def_5 <- lm(defence ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_def_5)

model_reb_5 <- lm(rebuilding ~ treatment + age + gender + country_origin_Ukraine, data = data)
summary(model_reb_5)
#####
```


*Correlation analysis*
```{r}
# Kherson liberation treatment: donations to rebuilding + humanitarian causes and joy
#####
# Calculate the average donations to rebuilding and humanitarian aid causes per subject
kherson_data <- data[data$treatment == "Kherson Liberation", ]
kherson_data$avg_donations_3 <- rowMeans(kherson_data[, c("rebuilding","humanitarian")])

# Calculate the correlation coefficient between "joy" and average donations
correlation_kherson <- cor(kherson_data$joy, kherson_data$avg_donations)
correlation_kherson
cor.test(kherson_data$joy, kherson_data$avg_donations)$p.value
#####

# Ukraine Shelling treatment: donations to defense cause and fear, anger
#####
#Fear
# Calculate the average donations to defense cause per subject
shelling_data <- data[data$treatment == "Ukraine Shelling", ]
shelling_data$avg_donations <- rowMeans(shelling_data[, c("defence")])

# Calculate the correlation coefficient between "fear" and average donations
correlation_shelling <- cor(shelling_data$fear, shelling_data$avg_donations)
correlation_shelling
cor.test(shelling_data$fear, shelling_data$avg_donations)$p.value

#Anger
correlation_shelling_ang <- cor(shelling_data$anger, shelling_data$avg_donations)
print(correlation_shelling_ang)
cor.test(shelling_data$anger, shelling_data$avg_donations)$p.value
#####

# Release POWs treatment: donations to rebuilding + humanitarian and relief
#####
# Calculate the average donations to rebuilding, medical, and humanitarian aid causes per subject
POWs_data <- data[data$treatment == "Release of POWs", ]
POWs_data$avg_donations <- rowMeans(POWs_data[, c("rebuilding", "humanitarian")])

# Calculate the correlation coefficient between "relief" and average donations
correlation_POWs <- cor(POWs_data$relief, POWs_data$avg_donations)
print (correlation_POWs)
cor.test(POWs_data$relief, POWs_data$avg_donations)$p.value
#####

# Drama theater treatment: donations to defence and sadness, disgust
#####
# Sadness
mariupol_data <- data[data$treatment == "Drama Theater", ]

# Calculate the correlation coefficient between the average of sadness & disgust and average donations
correlation_mariupol <- cor(mariupol_data$sadness, mariupol_data$defence)
print(correlation_mariupol)
cor.test(mariupol_data$sadness, mariupol_data$defence)$p.value

#Disgust
correlation_mariupol_dis <- cor(mariupol_data$disgust, mariupol_data$defence)
print(correlation_mariupol_dis)
cor.test(mariupol_data$disgust, mariupol_data$defence)$p.value
#####
```

*Pairwise t-tests*

